\section*{Conclusion}

\begin{frame}
  \sectionpage
\end{frame}

\begin{frame}{Fighting Byzantine Attacks in Federated Learning}
  \textbf{The proposed framework can:}
  \begin{itemize}
    \item Accurately cluster similar participants based on cross evaluations results.
    \item Mitigate label-flipping untargeted attacks via clustering.
    \item Mitigate most label-flipping targeted attacks, including colluding attackers (up to 80\% of poisoned data).
  \end{itemize}

  \pause
  \textbf{How generic?}
  \begin{itemize}
    \item Only few conditions: parametric models, locally owned evaluation set, a \alert<3>{small-scale use case}, and a \alert<3>{trusted central server}.
  \end{itemize}
\end{frame}


\begin{frame}{Future Work}
  \textbf{Future works:}
    \begin{itemize}
      \item Remove the central server dependency.
      \item Reduce the cross-evaluation overhead to extend applicability to cross device settings.
      \item Test the approach in more realistic heterogeneous settings.
    \end{itemize}
\end{frame}


\begin{frame}
  \centering\scshape\large Thank you for your attention!

  \vfill
  
  \normalshape\normalsize

  \textbf{RADAR: Model Quality Assessment for Reputation-aware\\ Collaborative Federated Learning}
  \medskip
  
  \raggedright
  \begin{itemize}
    \item A novel architecture for cross-silo FL, combining reputation and clustering to ensure model quality.
    \item An evaluation showing great coverage in the mitigated scenarios.
    \item Promising research directions towards trustable, decentralized, privacy-preserving collaborative learning.
  \end{itemize}

  \vfill

  \centering\small
  leo.lavaur@imt-atlantique.fr\\
  pierre-marie.lechevalier@imt-atlantique.fr

\end{frame}


